Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-01-10 WSSSPE4_report/WSSSPE4_report.tex
playiung with figure spacing
adding authors of sections that have appeared - info (affil, email, ORCID) needed

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

@@

\author{Daniel S.\ Katz$^{(1)}$,
Kyle E.\ Niemeyer$^{(2)}$,
Sandra Gesing$^{(3)}$,
Lorraine Hwang$^{(4)}$,
Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(3)}$ \note{info needed}}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu}

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[font=small]{caption}
\usepackage{varwidth}

@@

\author{Daniel S.\ Katz$^{(1)}$,
Kyle E.\ Niemeyer$^{(2)}$,
Sandra Gesing$^{(3)}$,
Lorraine Hwang$^{(4)}$,
Alice Allen$^{(5)}$,
Neil Chue Hong$^{(6)}$,
Anshu Dubey$^{(7)}$,
Jonah Miller$^{(8)}$,
Jean Salac$^{(9)}$,
Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: ?}
%
\thanks{{}$^{(3)}$ \note{info needed}}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: ?}
%
\thanks{{}$^{(5)}$ \note{info needed}}
%
\thanks{{}$^{(6)}$ \note{info needed}}
%
\thanks{{}$^{(7)}$ \note{info needed}}
%
\thanks{{}$^{(8)}$ \note{info needed}}
%
\thanks{{}$^{(9)}$ \note{info needed}}
